The CrypTool Script: \\ Cryptography, Mathematics and more \\ \vspace{30pt} {\large Background reading\\%*[-8pt] for the free eLearning program CrypTool\\ (8th edition -- distributed with CrypTool version 1.4.10)} \vspace{60pt}

### 2007-07-02 script/en/chapters/authors.tex
Update scripts: minimal correction

\paragraph{Figures:}
The figures ~\ref{NT_Fig_C1.3_EuclidsAlg-LinearCombinations}
till~\ref{NT_Fig_C5.3_PollardRho} give you an impression of the
educational tool ``NT'':

>>>>

\paragraph{Figures:}
The figures~\ref{NT_Fig_C1.3_EuclidsAlg-LinearCombinations}
till~\ref{NT_Fig_C5.3_PollardRho} give you an impression of the
educational tool ``NT'':

### 2007-07-02 script/en/chapters/primes.tex
Update scripts: minimal correction

% --------------------------------------------------------------------------
\pagebreak %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vskip +10 pt
\subsubsection{$f(n) = n^2 - 79 \cdot n + 1,601$}
\label{L-Polynomfunktion02-1601}   \label{SrcPrimArith1}
   This function\footnote{%
   See \hyperlink{PrimArith1}{Appendix A of this chapter} for the source code
   to compute the table using Pari-GP.\index{Pari-GP}
}
   delivers prime numbers for all values from $n=0$ to $n=79$.
Unfortunately $f(80) = 1,681 = 11 \cdot 151$ is not a prime number. To this
date, no function has been found that delivers more prime numbers in a row. On
the other hand, each prime occurs twice (first in the decreasing then in the
increasing sequence), which means that the algorithm delivers a total of 40
different prime values (these are the same ones as delivered by the function
in chapter~\ref{L-Polynomfunktion01-41})\footnote{%
   Another quadratic polynom, which delivers these primes, is: 
   $f(n) = n^2 - 9 \cdot n + 61$.\\
   Among the first 1000 sequence elements more than 50\% are prime
   (See \hyperlink{PrimArith2}{Appendix A of this chapter}).}.
$$
\begin{array}{|ll||ll|}
\hline
f(0)  = 1.601 & \mapsto {\rm ~prim}   &   f(26) =   223 & \mapsto {\rm ~prim} \\
f(1)  = 1.523 & \mapsto {\rm ~prim}   &   f(27) =   197 & \mapsto {\rm ~prim} \\
f(2)  = 1.447 & \mapsto {\rm ~prim}   &   f(28) =   173 & \mapsto {\rm ~prim} \\
f(3)  = 1.373 & \mapsto {\rm ~prim}   &   f(29) =   151 & \mapsto {\rm ~prim} \\
f(4)  = 1.301 & \mapsto {\rm ~prim}   &   f(30) =   131 & \mapsto {\rm ~prim} \\
f(5)  = 1.231 & \mapsto {\rm ~prim}   &   f(31) =   113 & \mapsto {\rm ~prim} \\
f(6)  = 1.163 & \mapsto {\rm ~prim}   &   f(32) =    97 & \mapsto {\rm ~prim} \\
f(7)  = 1.097 & \mapsto {\rm ~prim}   &   f(33) =    83 & \mapsto {\rm ~prim} \\
f(8)  = 1.033 & \mapsto {\rm ~prim}   &   f(34) =    71 & \mapsto {\rm ~prim} \\
f(9)  =   971 & \mapsto {\rm ~prim}   &   f(35) =    61 & \mapsto {\rm ~prim} \\
f(10) =   911 & \mapsto {\rm ~prim}   &   f(36) =    53 & \mapsto {\rm ~prim} \\
f(11) =   853 & \mapsto {\rm ~prim}   &   f(37) =    47 & \mapsto {\rm ~prim} \\
f(12) =   797 & \mapsto {\rm ~prim}   &   f(38) =    43 & \mapsto {\rm ~prim} \\
f(13) =   743 & \mapsto {\rm ~prim}   &   f(39) =    41 & \mapsto {\rm ~prim} \\
f(14) =   691 & \mapsto {\rm ~prim}   &   f(40) =    41 & \mapsto {\rm ~prim} \\              
f(15) =   641 & \mapsto {\rm ~prim}   &   f(41) =    43 & \mapsto {\rm ~prim} \\              
f(16) =   593 & \mapsto {\rm ~prim}   &   f(42) =    47 & \mapsto {\rm ~prim} \\              
f(17) =   547 & \mapsto {\rm ~prim}   &   f(43) =    53 & \mapsto {\rm ~prim} \\              
f(18) =   503 & \mapsto {\rm ~prim}   &   \cdots  &  \\                                       
f(19) =   461 & \mapsto {\rm ~prim}   &   f(77) = 1.447 & \mapsto {\rm ~prim} \\             
f(20) =   421 & \mapsto {\rm ~prim}   &   f(78) = 1.523 & \mapsto {\rm ~prim} \\             
f(21) =   383 & \mapsto {\rm ~prim}   &   f(79) = 1.601 & \mapsto {\rm ~prim} \\             
f(22) =   347 & \mapsto {\rm ~prim}   &   f(80) = 41 \cdot 41 & \mapsto {\rm ~NICHT~prim!} \\
f(21) =   383 & \mapsto {\rm ~prim}   &   f(81) = 41 \cdot 43 & \mapsto {\rm ~NICHT~prim!} \\ 
f(22) =   347 & \mapsto {\rm ~prim}   &   f(82) = 1.847 & \mapsto {\rm ~prim} \\             
f(23) =   313 & \mapsto {\rm ~prim}   &   f(83) = 1.933 & \mapsto {\rm ~prim} \\              
f(24) =   281 & \mapsto {\rm ~prim}   &   f(84) = 43 \cdot 47 &  \mapsto {\rm ~NICHT~prim!} \\
f(25) =   251 & \mapsto {\rm ~prim}   &   & \\
\hline
\end{array} 
$$

>>>>

% --------------------------------------------------------------------------
\pagebreak %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% \vskip +10 pt
\subsubsection{$f(n) = n^2 - 79 \cdot n + 1,601$}
\label{L-Polynomfunktion02-1601}   \label{SrcPrimArith1}
   This function\footnote{%
   See \hyperlink{PrimArith1}{Appendix A of this chapter} for the source code
   to compute the table using Pari-GP.\index{Pari-GP}
}
   delivers prime numbers for all values from $n=0$ to $n=79$.
Unfortunately $f(80) = 1,681 = 11 \cdot 151$ is not a prime number. To this
date, no function has been found that delivers more prime numbers in a row. On
the other hand, each prime occurs twice (first in the decreasing then in the
increasing sequence), which means that the algorithm delivers a total of 40
different prime values (these are the same ones as delivered by the function
in chapter~\ref{L-Polynomfunktion01-41})\footnote{%
   Another quadratic polynom, which delivers these primes, is: 
   $f(n) = n^2 - 9 \cdot n + 61$.\\
   Among the first 1000 sequence elements more than 50\% are prime
   (See \hyperlink{PrimArith2}{Appendix A of this chapter}).}.
$$
\begin{array}{|ll||ll|}
\hline
f(0)  = 1.601 & \mapsto {\rm ~prim}   &   f(26) =   223 & \mapsto {\rm ~prim} \\
f(1)  = 1.523 & \mapsto {\rm ~prim}   &   f(27) =   197 & \mapsto {\rm ~prim} \\
f(2)  = 1.447 & \mapsto {\rm ~prim}   &   f(28) =   173 & \mapsto {\rm ~prim} \\
f(3)  = 1.373 & \mapsto {\rm ~prim}   &   f(29) =   151 & \mapsto {\rm ~prim} \\
f(4)  = 1.301 & \mapsto {\rm ~prim}   &   f(30) =   131 & \mapsto {\rm ~prim} \\
f(5)  = 1.231 & \mapsto {\rm ~prim}   &   f(31) =   113 & \mapsto {\rm ~prim} \\
f(6)  = 1.163 & \mapsto {\rm ~prim}   &   f(32) =    97 & \mapsto {\rm ~prim} \\
f(7)  = 1.097 & \mapsto {\rm ~prim}   &   f(33) =    83 & \mapsto {\rm ~prim} \\
f(8)  = 1.033 & \mapsto {\rm ~prim}   &   f(34) =    71 & \mapsto {\rm ~prim} \\
f(9)  =   971 & \mapsto {\rm ~prim}   &   f(35) =    61 & \mapsto {\rm ~prim} \\
f(10) =   911 & \mapsto {\rm ~prim}   &   f(36) =    53 & \mapsto {\rm ~prim} \\
f(11) =   853 & \mapsto {\rm ~prim}   &   f(37) =    47 & \mapsto {\rm ~prim} \\
f(12) =   797 & \mapsto {\rm ~prim}   &   f(38) =    43 & \mapsto {\rm ~prim} \\
f(13) =   743 & \mapsto {\rm ~prim}   &   f(39) =    41 & \mapsto {\rm ~prim} \\
f(14) =   691 & \mapsto {\rm ~prim}   &   f(40) =    41 & \mapsto {\rm ~prim} \\              
f(15) =   641 & \mapsto {\rm ~prim}   &   f(41) =    43 & \mapsto {\rm ~prim} \\              
f(16) =   593 & \mapsto {\rm ~prim}   &   f(42) =    47 & \mapsto {\rm ~prim} \\              
f(17) =   547 & \mapsto {\rm ~prim}   &   f(43) =    53 & \mapsto {\rm ~prim} \\              
f(18) =   503 & \mapsto {\rm ~prim}   &   \cdots  &  \\                                       
f(19) =   461 & \mapsto {\rm ~prim}   &   f(77) = 1.447 & \mapsto {\rm ~prim} \\             
f(20) =   421 & \mapsto {\rm ~prim}   &   f(78) = 1.523 & \mapsto {\rm ~prim} \\             
f(21) =   383 & \mapsto {\rm ~prim}   &   f(79) = 1.601 & \mapsto {\rm ~prim} \\             
f(22) =   347 & \mapsto {\rm ~prim}   &   f(80) = 41 \cdot 41 & \mapsto {\rm ~NOT~prim!} \\
f(21) =   383 & \mapsto {\rm ~prim}   &   f(81) = 41 \cdot 43 & \mapsto {\rm ~NOT~prim!} \\ 
f(22) =   347 & \mapsto {\rm ~prim}   &   f(82) = 1.847 & \mapsto {\rm ~prim} \\             
f(23) =   313 & \mapsto {\rm ~prim}   &   f(83) = 1.933 & \mapsto {\rm ~prim} \\              
f(24) =   281 & \mapsto {\rm ~prim}   &   f(84) = 43 \cdot 47 &  \mapsto {\rm ~NOT~prim!} \\
f(25) =   251 & \mapsto {\rm ~prim}   &   & \\
\hline
\end{array} 
$$
